---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Insured-Analysis



The code is avaible in the `lol.R` file. 

With a series of data which correspond to the claims of an insurer in Monterrey. It is to analyze and combine the risks of the insurer's portfolio. This report is created as a support for the risk committee to know the influence of the claims with the variables that are known.

The first step is to take a look at our data.


```{r, include = FALSE}

data <- read.csv("insurance.csv")


```

```{r, echo = FALSE}
head(data)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.
