---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Insured-Analysis



The code is avaible in the `Insured-Analysis.R` file. 

With a series of data which correspond to the claims of an insurer in Monterrey. It is to analyze and combine the risks of the insurer's portfolio. This report is created as a support for the risk committee to know the influence of the claims with the variables that are known.

The first step is to take a look at our data.


```{r, include = FALSE}

data <- read.csv("insurance.csv")


```

```{r, echo = FALSE}
head(data)
```

* The kilometers variable describes the category of the number of kilometers driven per insured. 
1.- <1,000 km. 
2.- 1,000 -15,000 km. 
3.- 15,000 - 20,000 km. 
4.- 20,000 - 25,000 km. 
5.- 25,000 km. 

* The zone variable describes the municipality to which the insured belongs. 
1.- Monterrey. 
2.- San Pedro. 
3.- San Nicolas. 
4.- Escobedo. 
5.- Guadalupe.
6.- Garcia. 
7.- Others. 

* Variable Bonus: Number of years since the insured filed a claim +1

* Variable Make: Model of the insured car 1-8 represents a certain model and 9 represents the rest. 

* Insured variable: Number of insured per policy year.

* Claims variable: Number of claims made by the lot or insured.

### First descriptive analysis 

In order to understand in a correct way the data being handled, an analysis of the dataphrame was made. A sampling of the variables that are in our model is made, as well as the relationship that they have with each other. 


```{r pressure, echo = FALSE}
columnas_hist <- c("Payment", "Claims", "Kilometres")

for (column in columnas_hist) {
   hist(data[,column], col="#198CE7", xlab=column,main=paste0("Histogram of ",column))
}
```

#### a)Sum of insured per kilometer:

```{r echo = FALSE}
grafos <- c(1,2,3,4,5)
primero <- c()
segundo <- c()
tercero <- c()
for (i in c(1,2,3,4,5)) {
  primero[i] <- sum(subset(data, Kilometres == i, select = c("Insured")))  
}
barplot(primero, names =grafos, xlab = "Kilometers",  ylab = "Sum of Insured", col = c("blue","red","green","yellow","black"))
```

#### b)Sum of payments per Zone: 

```{r echo = FALSE}
grafis <- c(1,2,3,4,5,6,7)
for (i in c(1,2,3,4,5,6,7)) {
  primero[i] <- sum(subset(data, Zone == i, select = c("Payment")))  
}
barplot(primero, names=grafis ,xlab = "Zone",  ylab = "Sum of Payments", col = c("blue","red","green","yellow","black"))
```

#### c)Sum of claims per Model:
```{r echo = FALSE}

grafes <- c(1,2,3,4,5,6,7,8,9)
for (i in c(1,2,3,4,5,6,7,8,9)) {
  primero[i] <- sum(subset(data, Make == i, select = c("Claims")))  
}
barplot(primero, names=grafes ,xlab = "Models",  ylab = "Sum of Claims ", col = c("blue","red","green","yellow","black"))
```

A more exhaustive analysis of each variable as well as the relationship of one to the other can be found at in the `Insured-Analysis.R` file. 

### Correlation with the variable payments

For the insurance company, it is essential to see the relationship between the payment variable and the other variables, so we studied the correlation between the number of claims and the number of years in the portfolio in order to focus our efforts on strengthening everything that improves the payments received.

Making a correlation matrix we can see the relationship of one variable to another.

```{r, include = FALSE}
library(corrplot)
correlacion<-round(cor(data),1)

```

```{r echo = FALSE}
corrplot(correlacion, method="number", type="upper")
```

It can be seen that the variables with the highest correlation with payments are Insured and claims. Therefore a scatterplot of these variables was made. 


```{r echo = FALSE}
plot(data$Insured,data$Payment, xlab = "Insured",  ylab = "Payments" )
plot(data$Claims,data$Payment, xlab = "Claims",  ylab = "Payments")

```

```{r echo = FALSE}
pago_especial <- c()

for (i in c(1,2,3,4,5)) {
  primero_chale <- sum(subset(data, Kilometres == i, select = c("Insured")))
  segundo_chale <- sum(subset(data, Kilometres == i, select = c("Payment")))  
  pago_especial[i] <- primero_chale/segundo_chale

}

barplot(pago_especial, names =grafos, xlab = "Kilometros", ylab= "Pago especial")

pago_especial1 <- c()
grafis <- c(1,2,3,4,5,6,7)
for (i in c(1,2,3,4,5,6,7)) {
  primero_chale1 <- sum(subset(data, Zone == i, select = c("Insured")))
  segundo_chale1<- sum(subset(data, Zone == i, select = c("Payment")))  
  pago_especial1[i] <- primero_chale1/segundo_chale1
}

barplot(pago_especial1, names =grafis, xlab = "Municipio", ylab= "Pago especial")

pago_especial2 <- c()
grafis <- c(1,2,3,4,5,6,7)
for (i in c(1,2,3,4,5,6,7)) {
  primero_chale2 <- sum(subset(data, Bonus == i, select = c("Insured")))
  segundo_chale2<- sum(subset(data, Bonus == i, select = c("Payment")))  
  pago_especial2[i] <- primero_chale2/segundo_chale2
}

barplot(pago_especial2, names =grafis, xlab = "Bono", ylab= "Pago especial")
```