---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Insured-Analysis



The code is avaible in the `lol.R` file. 

With a series of data which correspond to the claims of an insurer in Monterrey. It is to analyze and combine the risks of the insurer's portfolio. This report is created as a support for the risk committee to know the influence of the claims with the variables that are known.

The first step is to take a look at our data.


```{r, include = FALSE}

data <- read.csv("insurance.csv")


```

```{r, echo = FALSE}
head(data)
```

The kilometers variable describes the category of the number of kilometers driven per insured. 
1.- <1,000 km. 
2.- 1,000 -15,000 km. 
3.- 15,000 - 20,000 km. 
4.- 20,000 - 25,000 km. 
5.- 25,000 km. 

The zone variable describes the municipality to which the insured belongs. 
1.- Monterrey. 
2.- San Pedro. 
3.- San Nicolas. 
4.- Escobedo. 
5.- Guadalupe.
6.- Garcia. 
7.- Others. 

Variable Bonus: Number of years since the insured filed a claim +1

Variable Make: Model of the insured car 1-8 represents a certain model and 9 represents the rest. 

Insured variable: Number of insured per policy year.

Claims variable: Number of claims made by the lot or insured.

In order to easily observe our data, a descriptive analysis of the variables is made through histograms.

```{r pressure, echo = FALSE}
columnas_hist <- names(data)

for (column in columnas_hist) {
   hist(data[,column], col="#198CE7", xlab=column,main=paste0("Histogram of ",column))
}
```

To have a clear idea of the correlation between all the variables in terms of kilometers, municipality and model.
The following graphs were made. 

a)Sum of insured per kilometer:

```{r echo = FALSE}
grafos <- c(1,2,3,4,5)
primero <- c()
segundo <- c()
tercero <- c()
for (i in c(1,2,3,4,5)) {
  primero[i] <- sum(subset(data, Kilometres == i, select = c("Insured")))  
}
barplot(primero, names =grafos, xlab = "Kilometers",  ylab = "Sum of Insured", col = c("blue","red","green","yellow","black"))
```
